\newpage

```{r datawrangling-04-data, echo=FALSE, warning=FALSE, message=FALSE}
################################################################################
# General ----------------------------------------------------------------------
################################################################################

# datasets to reference in the text
candidates <- accounts %>%
  filter(!is.na(gender))

partyaccounts <- accounts %>%
  filter(is.na(gender))

################################################################################
# For Plot Percentage Account --------------------------------------------------
################################################################################

# datawrangling ----------------------------------------------------------------

candidates2021 <- candidates2021_raw %>%
  mutate(name = paste(firstname, lastname),
         gender = recode(gender,
                         "w" = "female",
                         "m" = "male",
                         "d" = "diverse"),
         party = recode(party,
                        "DIE LINKE" = "LINKE"),
         twitter_active = ifelse(is.na(screen_name1), 0, 1)) %>%
  rename(twitter_handle = screen_name1,
         listed_candidate = isListed,
         direct_candidate = isDC,
         region = state) %>%
  select(name, twitter_handle, gender, party, district_name, district_number,
         region, incumbent, listed_candidate, direct_candidate, twitter_active)


# percentage with twitter account by party -------------------------------------
party_totals <- candidates2021 %>%
  group_by(party) %>%
  summarize(total = n())

percentage.accounts <- candidates2021 %>%
  group_by(party, twitter_active) %>%
  summarize(count = n()) %>%
  left_join(party_totals, by = "party") %>%
  mutate(percentage = count / total * 100,
         party = factor(party,
                        levels = c("LINKE", "GRÜNE", "SPD", "FDP",
                                   "CDU", "CSU", "AfD"))) %>%
  ungroup()

# variables for referencing in text --------------------------------------------
gruene_active_percentage <- percentage.accounts %>%
  filter(party == "GRÜNE" & twitter_active == 1) %>%
  pull(percentage)

cdu_active_percentage <- percentage.accounts %>%
  filter(party == "CDU" & twitter_active == 1) %>%
  pull(percentage)
```

# Data

In order to collect the data for analysis, I first obtained the Twitter handles for all relevant accounts using two hand curated datasets: [@konigEPINetzTwitterPoliticians2022] and [@saltzerTwitterAccountsCandidates2021]. These datasets not only provide the Twitter handles for candidates, politicians, and parties but also offer valuable metadata, including party affiliation, age, and other relevant information. Then I used the Twitter API to crawl all tweets and retweets posted by the accounts within a one year time frame before and after the election for the 20th German Bundestag (federal parliament) on the September 26, 2021.

As a result the final dataset employed contains `r format(nrow(tweets), big.mark = ".", scientific = FALSE)` tweets from from `r format(nrow(candidates), big.mark = ".", scientific = FALSE)` candidates and `r format(nrow(partyaccounts), big.mark = ".", scientific = FALSE)` party accounts affiliated with the SPD, CDU, FDP, Linke, Grüne and AfD. A detailed descriptions of the variables is provided in Table \ref{tab:apptable}.

## Descriptives

Politicians use Twitter extremely unevenly, and systematic differences between the parties are apparent. Representatives from conservative parties with an older electorate tend to use more *traditional* campaign media strategies, whereas politicians affiliated with progressive parties that attract a younger demographic, tend to utilize *modern* campaign media platforms such as Twitter, Instagram, and TikTok **(CITATION)**.

This is trend holds true for German politicians as well. As shown in Figure `@ref(fig:plot-percentage-account)`, `r round(gruene_active_percentage, 1)`% Grüne candidates have an account on Twitter, compared to a substantially lower `r round(cdu_active_percentage, 1)`% of CDU candidates.

```{r plot-percentage-account, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Percentage of Candidates with an Account on Twitter", fig.pos="H"}
ggplot(data = percentage.accounts, aes(x = party,
             y = percentage,
             fill = interaction(party, factor(twitter_active)))) +
  geom_bar(stat = "identity",
           position = position_dodge(width = .5)) +
  geom_text(data = . %>% filter(twitter_active == 1),
            aes(x = party, y = percentage, label = sprintf("%.1f", percentage)),
            position = position_dodge(width = .5),
            vjust = -0.5,
            size = 3,
            family = "LM Roman 10",
            hjust = -.02) +
  labs(x = "",
       y = "",
       title = "",
       legend = "",
       caption = "Note: The party-colored bars represent the percentage of candidates with a Twitter account, while the grey bars\nindicate the percentage without one.") +
  guides(fill = guide_legend(title = NULL)) +
  scale_fill_manual(values = c("LINKE.0" = "#C0C0C0AA", "LINKE.1" = "#BE3075",
                               "GRÜNE.0" = "#C0C0C0AA", "GRÜNE.1" = "#1AA037",
                               "SPD.0" = "#C0C0C0AA", "SPD.1" = "#E3000F",
                               "FDP.0" = "#C0C0C0AA", "FDP.1" = "#FFEF00",
                               "CDU.0" = "#C0C0C0AA", "CDU.1" = "#000000",
                               "CSU.0" = "#C0C0C0AA", "CSU.1" = "#0570C9",
                               "AfD.0" = "#C0C0C0AA", "AfD.1" = "#0489DB"),
                    labels = rep(c("No Twitter", "Has Twitter"), 7)) +
  scale_y_continuous(limits = c(0, 80),
                     breaks = seq(0, 80, 10),
                     labels = scales::percent(seq(0, .8, 0.1))) +
  theme_bw() +
  theme(legend.position = "none",
        plot.caption = element_text(hjust = 0,
                                  size = 8,
                                  margin = margin(t = 0)),
        text = element_text(family = "LM Roman 10"))

# variables for referencing in text --------------------------------------------
gruene_active_percentage <- percentage.accounts %>%
  filter(party == "GRÜNE" & twitter_active == 1) %>%
  pull(percentage)

cdu_active_percentage <- percentage.accounts %>%
  filter(party == "CDU" & twitter_active == 1) %>%
  pull(percentage)
```



```{r plot-tweets-amounty-byparty, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Number of Tweets posted by Party", fig.pos="H"}
dot_separator <- label_number(big.mark = ".")

tweets %>%
  group_by(party) %>%
  summarise(tweet_count = n()) %>%
  mutate(party = factor(party,
                        levels = c("LINKE", "GRUENE", "SPD", "FDP",
                                   "CDU", "CSU", "AfD"))) %>%
  ungroup() %>%
  mutate(party = reorder(party, tweet_count, FUN = max)) %>% # Reorder the factor levels
  ggplot(aes(x = party,
             y = tweet_count,
             fill = party)) +
  geom_bar(stat = "identity", width = .6) +
  geom_text(aes(label = comma(tweet_count, big.mark = ".")),
          hjust = -0.5,
          size = 3,
          family = "LM Roman 10") +
  labs(x = "",
       y = "",
       title = "",
       subtitle = "",
       legend = "") +
  guides(fill = guide_legend(title = NULL)) +
  scale_fill_manual(values = c("LINKE" = "#BE3075",
                               "GRUENE" = "#1AA037",
                               "SPD" = "#E3000F",
                               "FDP" = "#FFEF00",
                               "CDU" = "#000000",
                               "CSU" = "#0570C9",
                               "AfD" = "#0489DB")) +
  scale_y_continuous(limits = c(0, 300000),
                     breaks = seq(0, 300000, 50000),
                     labels = dot_separator) +
  theme_bw() +
  theme(text = element_text(family = "LM Roman 10"),
        legend.position = "none",
        plot.caption = element_text(hjust = 0,
                                    size = 8,
                                    face="italic",
                                    margin = margin(t = 8))) +
  coord_flip()
```

